Robust calibration of numerical models based on relative regret

### 2020-10-25 response.tex

\documentclass[a4paper,11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{amsmath}
\usepackage{bm}
\usepackage{amsfonts}
\usepackage{graphicx}
\usepackage{geometry}
\usepackage[utf8]{inputenc}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{tikz}
\usepackage{calc}
\usepackage{caption}
% \usepackage{zref-xr}
% \externaldocument{article}
\usepackage{easy-todo}
\usepackage{comment}
\usepackage{lipsum}
\usepackage{bbm}
\usepackage{fancyhdr}
\usepackage{tikz}
\usepackage{pdfpages}
\newcommand{\Var}{\mathbb{V}\text{ar}}
\newcommand{\Ex}{\mathbb{E}}
\newcommand{\Prob}{\mathbb{P}}
\DeclareMathOperator*{\argmin}{arg\,min \,}
\DeclareMathOperator*{\argmax}{arg\,max \,}
\usepackage{hyperref}
\usepackage{booktabs}

\begin{document}
\title{JCOMP-D-20-00132: Authors' response to reviewers:\\
  Robust calibration of numerical models based on relative regret
}

\maketitle
We would like to thank the reviewer for their review. Their comments helped us clarify and improve some points in the manuscript, and we got to study some aspects of the problem that we have not necessarily considered before.

In the revised manuscript, we adressed the concerns raised by the reviewer, and made some adjustements on the original text. The changes to the original text have been highlighted in {\color{teal}teal}.
\section{Reply to the reviewers}
\begin{enumerate}
\item\textit{In the existing literature, there are many robust estimation approaches, such as distributionally robust methods and the regularization strategy to improve robustness. What are the specific values of relative regret in case studies?} \textit{ Why this regret metric matter in real practice? The novelty should be highlighted in the revised manuscript by comparing with the above mentioned approaches.}

    In this work, as we assumed that $\mathbf{U}$ is perfectly known, so we did not consider distributional robustness, as now explained l~.84.
    In this work, we wanted to avoid an \emph{aggregation} approach, where the value of the cost function is integrated with respect to the environmental variable (such as moment optimisation).
    We wanted instead to consider separately each optimization problem corresponding to each $\mathbf{u}\in \mathbb{U}$, and measure the similarity of the cost function at a value $J(\mathbf{k},\mathbf{u})$ with $J^*(\mathbf{u})$. As now mentioned l.~282, this is linked to the optimisation of the Value-at-Risk, or equivalently, to the minimisation of a quantile, l.~345. This metric allows us to control the risk in terms of deviation from the optimal value.% . For a couple $(p=.90, \alpha_p=1.1)$, this approach allow us to make the following statement true: in 90\% percent of the cases, the objective function does not deviate more than $10\%$ from its optimal value.
 % l.~109 l.~233, l.~264

   % séparer questions, et valider
  % We 
\item \textit{For Equation (1), how do the authors choose the sample space U. How should one construct it?}

We assume that the aleatoric uncertainties, modelled as a random variable $\mathbf{U}$, come from expert knowledge, and then its distribution and its sample space is assumed to be known. This is now explicitely stated l.~62. If it is not known, we refer the reader as advised to the article mentioned in the comment \# 4
\item \textit{In Page 2, the authors mentioned that "set to be estimated to reduce epistemic errors. The aleatoric uncertainties are modelled as a random vector". Did the authors implicitly assume that the aleatoric uncertainty is independent with the epistemic uncertainty? The authors should clarify this issue.}

  We assume indeed that the epistemic and aleatoric uncertainties are independent, due to the fact that the aleatoric uncertainties come from some external forcings of models, and that the choice of our control parameter does not affect the aleatoric uncertainties. This is now explicitly addressed in the introduction (l.67).

\item \textit{The literature review on optimization under uncertainties is relatively good. However, it still needs improvement to reflect the recent advances in this area. To help the reader get to know the state-of-the-art, the authors should add the work on "optimization under uncertainty in the era of big data and deep learning" in the revised manuscript.
  }

  We indeed overlooked the problem of the possibly unknown distribution of $\mathbf{U}$. The paper is now cited in the literature review l.~64. In this section, we mention especially data-driven methods to model the aleatoric uncertainties, and mention now the case of distributional robustness.

\item \textit{For the proposed "relative regret-based family of estimators", the authors seem to know the probability distribution of u perfectly, this is impractical for real applications. Please consider some realistic applications where this distribution can be known and why it can be known perfectly.
  }

  We added a small discussion on the presumed knowledge of the distribution of $\mathbf{U}$ in the introduction l.~60. The  uncertainties are supposed to be known reasonably well, as they may come from empirical observations, or expert knowledge, in order to have relevant probabilistic description.

\item \textit{Why only consider relative regret? How about absolute regret (the difference between the estimated one and the optimal value)? Should the authors use the worst-case relative regret if only uncertainty set is known. The authors should carefully address this issue.}

  We added a comparison between relative and additive regret p.~13, l.~261, and motivated the choiceof the relative regret: choosing the relative regret allows the decider to put less weight on the region around $\mathbf{k}^*(\mathbf{u})$ when $\mathbf{u}$ corresponds to a bad situation (\textit{i.e.} when $J^*(\mathbf{u})$ is large). We hope this is clarified by the explanation l.~262.

\item \textit{In Figure 4, it is difficult to identify the difference in color of the last two lines. The authors should revise the figure accordingly.}

  The colors and linestyles in Figure 4 have been updated for more clarity.

\item \textit{ For Equation (19), if the probability distribution Pu is perfectly known for the chance constraint, it seems to be trivial to the sample average approximation (SAA) method. How can the authors quantify the error of using this approximation method? Will it have an impact on the calibration results? The authors should explain it in detail.}

  Eq.~(19) is now Eq.~(22) in the revised document. We introduced in Eq.~(25) the Sample Average Approximation of the Eq.~(20). Using SAA, the resulting $\hat{\alpha}_1$ is a lower bound on the true value. Furthermore, we can also use this estimated value to get a probabilistic upper bound on $\alpha_p$ for the prescribed level $p=(\eta/2)^{1/N}$, meaning that the approximated solution will be at least feasible at such a level with probability $1-\eta$.

\item \textit{The authors need to justify why their proposed approach is robust calibration based on a stochastic approach (using probability distribution and chance constraint)?}
From a random objective function $J(\mathbf{k}, \mathbf{U})$, we introduce the relative-regret which is a normalized quantity (l.~270). Our approach is then to introduce a chance-constraint on this relative-regret, as done Eq.~(20), in order to be able to control the deviations relative to the optimal value with some probability. In the case of almost-surely verified constraints (Eq.~(21) and (22)), this approach is quite similar to optimising in the worst-case the relative-regret, as highlighted Eq.~(24). Given $p$ and $\alpha_p$, our approach look then to minimise the relative-regret for the proportion $p$ of best-cases as now explained l.~286. We also highlighted the principle and novelty of our approach in the abstract l.11, and in the conclusion l.~557.

\end{enumerate}

\section{Summary of the changes}
\emph{Abstract (p.1)}
\begin{itemize}  
\item l.~5-8: clarified the distinction between control parameters, and uncontrollable random variables
\item l~.11-16: highlighted the role and novelty of the relative regret in this article
\end{itemize}
\emph{Introduction (p.1)}
\begin{itemize}
\item l.~34-37: added source of aleatoric uncertainties for ocean modelling
\item l.~38-48: added effect of omitting the uncertainties in problems
\item l.~48-51: added examples of the necessity of taking into account uncertainties, from a risk management perspective
\item l.~52-56: added different vocabulary found in the literature which convey the same idea
\item l.~57: fixed some typos and english mistakes.
\item l.~60: we explicit the knowledge of the distribution of $\mathbf{U}$.
\item l.~64: added state-of-the-art strategies to model aleatoric uncertainties and citation to Ning \& You.
\item l~.66-68: we clarify that the distributinto $\mathbf{U}$ is not dependent on the value of $\mathbf{k}$
\item l.~73: a reference to an exemple of such a cost function is added
\item l.~82: fixed typo
\item l.~84-85: added the mention of distributional robustness 
\item l.~92: added mention of overcalibration
\item l.~83: typo
\item l.~96,98,99: reformulation for clarity
\item l.~109: added rationale of the relative regret
\item l.~115: typo
\end{itemize}
\emph{Section 2 (p.5)}
\begin{itemize}
\item l.~119: change for clarification
\end{itemize}
\emph{Section 3.1 (p.11)}
\begin{itemize}
\item l.~232-238: clarification of the construction and definition of the relative-regret 
\item l.~253: added reminder that $\mathbf{K}^*$ is discrete.
\item l.~261-272: comparison between additive and relative regret, and justification of the use of relative-regret
\item l.~278-279: formulation of the problem in terms of chance-constraints in Eq.~(20)
\item l.~281-282: clarification of the link with the Value-at-Risk 
\item l.~283-286: interpretation of $\alpha_p$ in terms of bounding probabilistically the relative-error
\item l.~287-288: rewrote the definition of the RRE
\item l.~289-291: typo and english reformation
\item Figure 4 (p.14): changed linestyle, and added quick interpretation in the caption 
\item l.~293: added small synthesis on the properties of the RRE
\end{itemize}
\emph{Section 3.2 (p.14)}
  \begin{itemize}
\item l.~301: added subsection Almost-surely bounded relative-regret
\item l.~302-308: formulation of the a.s.\ bounded relative-regret in terms of chance constraint in Eq.~(21) and property verified by $\mathbf{k}_1$ and $\alpha_1$
\item l.~309-314: link with uncertain set and Savage's minimax approach for decision under uncertainty
\item l.~315-317: SAA formulation of the a.s. bounded constraint
\item l.~317-325: Probabilistic bounding of $\alpha_1$, and level $p=(\eta/2)^{1/N}$ guaranteed probabilistically
\item l.~330-333: clarify formulation of the general case $p \leq 1$
\item l~.336-337: estimation of $\Gamma_\alpha$ with indicator functions (Eq.~(27))
\item l~.339: possibility of unsatisfactory $(p, \alpha_p)$
\item l.~344: minimization of the quantile of order $p$ of the ratio $J / J^*$.
\end{itemize}
 \emph{Conclusion (p.31)}
\begin{itemize}
\item l~.557-564: summary of the robustness aspect of the RRE
\item l~.578-580: reformulation of the sequential design of experiment strategies.
\end{itemize}

\end{document}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:

### 2020-10-25 source_files/article.tex
accepted version + zip of src

\documentclass[preprint, review, 1p]{elsarticle}

@@

%% For including figures, graphicx.sty has been loaded in
%% elsarticle.cls. If you prefer to use the old commands
%% please give \usepackage{epsfig}
% \usepackage{jcomp}
% \usepackage{framed,multirow}
%% The amssymb package provides various useful mathematical symbols
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
%% The amsthm package provides extended theorem environments
%% \usepackage{amsthm}

%% The lineno packages adds line numbers. Start line numbering with
%% \begin{linenumbers}, end it with \end{linenumbers}. Or switch it on
%% for the whole article with \linenumbers.
%% \usepackage{lineno}
\usepackage{graphicx}
\usepackage{booktabs}
% À changer
\newcommand{\yobs}{\mathbf{y}^o}
\DeclareMathOperator*{\argmin}{arg\,min \,}
\DeclareMathOperator*{\argmax}{arg\,max \,}
\newcommand{\Var}{\mathbb{V}\textrm{ar}}
\newcommand{\Ex}{\mathbb{E}}
\newcommand{\Prob}{\mathbb{P}}
\newcommand{\Cov}{\textsf{Cov}}
\newcommand{\tra}{\mathrm{tr}}
\newcommand{\kmean}{{\mathbf{k}}_{\Ex}}
\newcommand{\hatkmean}{\hat{\mathbf{k}}_{\Ex}}
\newcommand{\kvar}{{\mathbf{k}}_{\mathbb{V}}}
\newcommand{\hatkvar}{\hat{\mathbf{k}}_{\mathbb{V}}}
\newcommand{\kmpe}{{\mathbf{k}}_{\mathrm{MPE}}}
\newcommand{\hatkmpe}{\hat{\mathbf{k}}_{\mathrm{MPE}}}
\newcommand{\kest}{\hat{\mathbf{k}}}
\newcommand{\RRE}{RRE}
\newcommand{\checkap}{{\alpha}_p}
\newcommand{\checka}{{\alpha}}
\newcommand{\checkk}{\mathbf{k}}
\newcommand{\checkkp}{{\mathbf{k}}_p}
\newcommand{\hatkp}{\hat{\mathbf{k}}_p}
\newcommand{\Kspace}{\mathbb{K}}
\newcommand{\Uspace}{\mathbb{U}}
\newcommand{\JBH}{J_{\mathrm{BH}}}
\newcommand{\JBHS}{J_{\mathrm{BHswap}}}

\newcommand{\arthur}[1]{{\itshape\color{cyan} ({#1})}}
\newcommand{\elise}[1]{{\itshape\color{red} ({#1})}}
\newcommand{\victor}[1]{{\itshape\color{green} ({#1})}}
\usepackage{url}
\usepackage{xcolor}
\definecolor{newcolor}{rgb}{.8,.349,.1}

\newlength{\minisize}
\setlength{\minisize}{3cm}
\newlength{\singlecolumnsize}
\setlength{\singlecolumnsize}{9cm}
\newlength{\onehalfcolumn}
\setlength{\onehalfcolumn}{14cm}
\newlength{\fullwidth}
\setlength{\fullwidth}{19cm}

@@

\begin{document}

%% Title, authors and addresses

@@

\begin{abstract}
%% Text of abstract
Classical methods of parameter estimation usually imply the minimisation of an objective function, that measures the error between some observations and the results obtained by a numerical model. In the presence of random inputs, the objective function becomes a random variable, and notions of robustness have to be introduced.

In this paper, we are going to present how to take into account those uncertainties by defining a family of calibration objectives based on the notion of relative-regret with respect to the best attainable performance given the uncertainties and compare it with the minimum in the mean sense, and the minimum of variance.
\end{abstract}

@@

%----------------------------------------------------------------------------
Numerical models are widely used to study or forecast natural phenomena and improve industrial processes. However, by essence models only partially represent reality and sources of uncertainties are ubiquitous (discretisation errors, missing physical processes, poorly known boundary conditions).
%Many physical phenomena are modelled numerically in order to better understand and/or to predict their behaviour. Because of the complexity and or ignorance of the underlying physics, numerical models are imperfect representations of the reality. 
%
%Various sources of uncertainties can corrupt the model quality, such as the discretisation of the domain, or presence of  small scale phenomena that can not be fully represented. 
Moreover, such uncertainties may be of different nature. 
\cite{walker_defining_2003} proposes to consider two categories of uncertainties. On the one hand aleatoric uncertainties,  coming from the inherent variability of a phenomenon, e.g.\ intrinsic randomness of some environmental variables. On the other hand, epistemic uncertainties coming from a lack of knowledge about the properties and conditions of the phenomenon underlying the behaviour of the system under study.
The latter can be accounted for through the introduction of ad-hoc correcting terms in the numerical model, that need to be properly estimated. Thus, reducing the epistemic uncertainty can be done through parameters estimation approaches. 
%when one is having observations of the reality. 
This is usually done using optimal control techniques, leading to an optimisation of a well chosen cost function which is typically built as a comparison with reference observations.
%
An application of such an approach, in the context of ocean circulation modeling, is the estimation of ocean bottom friction parameters in~\cite{das_estimation_1991} and~\cite{boutet_estimation_2015}.

If parameters to be estimated are not the only source of uncertainties, their optimal control 
%However, in the presence of other sources of uncertainties, parameter estimation 
is doomed to overfit the data, \emph{e.g} to artificially introduce errors in the controlled parameter to compensate for other sources. If such uncertainties are of aleatoric nature, then the parameter estimation is only optimal for the observed situation, and may be very poor in other configurations, phenomenon coined as \textit{localized optimisation} in~\cite{huyse_free-form_2001}.
%A methodology based on the Hessian matrix has been described in~\cite{ribaud_krigeage_2018-1}.
%\arthur{L\`A AUSSI UNE REF SERAIT BIENVENUE}. 
Taking into account aleatoric uncertainties in optimisation problems takes several names, including \textit{robust optimisation}, \textit{robust design} in~\cite{lelievre_consideration_2016}, or \textit{optimisation under uncertainties} \citep{petrone_robustness_2011, seshadri_density-matching_2014,cook_horsetail_2018}.

@@

%Taking into account aleatoric uncertainties while calibrating the model (reducing epistemic uncertainties) is often referred as {\it robust control problem} in the literature (see for instance, \arthur{REFs}), or optimization under uncertainties \citep{petrone_robustness_2011, seshadri_density-matching_2014,cook_horsetail_2018}.

Let's denote $\mathbf{k} \in \Kspace$ the parameter set to be estimated to reduce epistemic errors. The aleatoric uncertainties are modelled as a random vector $\mathbf{U}$ whose sample space is $\Uspace$. The probability measure of $\mathbf{U}$ is $\Prob_{\mathbf{U}}$, and its density, if it exists, is $p_{\mathbf{U}}$. \victor{\#3: Did the authors implicitly assume that the aleatoric uncertainty is independent with the epistemic uncertainty? The authors should clarify this issue.}%Furthermore, $\mathbf{u}^t$ (used to generate $\mathbf{y}^{\mathrm{obs}}$) is sampled from $\mathbf{U}$.
%
The cost function $J(\mathbf{k}, \mathbf{U})$ is a random variable in this context. %, quantity of interest summarising what we aim to represent with our numerical system $J(\mathbf{k}, \mathbf{U})$ is a random variable that will be further designed as the cost function. 
It is most often defined as the squared norm of a given function $\mathcal{G}(\mathbf{k}, \mathbf{U})$% involving the numerical model.
\victor{\# 2: How should one choose and/or construct $U$ ?}
\begin{align}
  \label{eq:def_cost_fun}
  J(\mathbf{k},\mathbf{U}) & = \frac12\|\mathcal{G}(\mathbf{k}, \mathbf{U})\|^2
  \end{align}
%$J$ is possibly complemented by a regularisation function that is omitted here for the sake of clarity. 
For instance, in data assimilation, $J$ describes a distance between the output of the numerical model and given observed data, plus generally some regularization terms.
%Calibrating the numerical models consists in the computation of $\kest$ verifying
%\begin{equation}
%  \label{eq:khat_def}
%  \kest = \argmin_{\mathbf{k} \in \Kspace} J(\mathbf{k}, \mathbf{u})
%\end{equation}
%\elise{la il y a un soucis car J(k,U) est une variable aleatoire donc on sait pas ce que ca veut dire de prendre le min} \victor{ici ça serait mieux de mettre un $\mathbf{u}^b$}
%
%where $J$ is then an objective function to minimise,
 %
%For a given $\mathbf{k}$, $J(\mathbf{k},\mathbf{U})$ is a random variable. The main point is to be able to compute a value $\mathbf{k}$ that ``minimises'' in a certain sense the random variable $J(\mathbf{k},\mathbf{U})$. \elise{a revoir. un v.a. ne se minimise pas} 
%
For a practical purpose, we assume that for every realisation $\mathbf{u}\in\Uspace$ of $\mathbf{U}$, % $\forall~ \mathbf{u}$ a realisation of $\mathbf{U}$
finding ${\mathbf{k}}_{\mathbf{u}}\in \Kspace$ that minimises the cost function $\mathbf{k}\mapsto J(\mathbf{k}, \mathbf{U}=\mathbf{u})$ is a well-posed problem, and that the optimum is unique.
Additionally, the following assumptions are made: the cost function is strictly positive, and $\forall~  \mathbf{k} \in \Kspace$, the random variable $J(\mathbf{k},\mathbf{U})$ has finite first- and second-order moments.

In this paper, we aim at finding $\kest$ a {\it robust\/} estimator of $\mathbf{k}$.
The definition of robustness differs depending on the context in which it is used. Indeed, one definition of the robustness of an estimate is a measure of the sensibility of said estimate to outliers~\citep{huber_robust_2011}. This lead to the introduction of robust norms in data assimilation \citep{rao_robust_2015}. %The point of this norm is to assume Gaussian distribution for small errors (the usual $L_2$ norm), while the large errors are assumed to be Laplace distributed (so the $L_1$ norm).
In a Bayesian framework, robustness may refer to the sensitivity to a wrong specification of the priors~\citep{berger_overview_1994}.
%
Throughout this paper, 
%we define robustness as the ability of $\kest$ to perform reasonably well under different operating conditions (i.e.\ different $\mathbf{u}$).
robust has to be understood as satisfactory for a broad range of $\mathbf{u}$, and/or as insensitive as possible to uncertainties encompassed in $\mathbf{U}$.

>>>>

\documentclass[preprint,review, 1p]{elsarticle}

@@

%% For including figures, graphicx.sty has been loaded in
%% elsarticle.cls. If you prefer to use the old commands
%% please give \usepackage{epsfig}
% \usepackage{jcomp}
% \usepackage{framed,multirow}
%% The amssymb package provides various useful mathematical symbols
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{soul}
\usepackage{verbatim}
%% The amsthm package provides extended theorem environments
%% \usepackage{amsthm}

%% The lineno packages adds line numbers. Start line numbering with
%% \begin{linenumbers}, end it with \end{linenumbers}. Or switch it on
%% for the whole article with \linenumbers.
\usepackage[mathlines]{lineno}

\usepackage{graphicx}
\usepackage{booktabs}
% À changer
\newcommand{\yobs}{\mathbf{y}^o}
\DeclareMathOperator*{\argmin}{arg\,min \,}
\DeclareMathOperator*{\argmax}{arg\,max \,}
\newcommand{\Var}{\mathbb{V}\textrm{ar}}
\newcommand{\Ex}{\mathbb{E}}
\newcommand{\Prob}{\mathbb{P}}
\newcommand{\Cov}{\textsf{Cov}}
\newcommand{\tra}{\mathrm{tr}}
\newcommand{\kmean}{{\mathbf{k}}_{\Ex}}
\newcommand{\hatkmean}{\hat{\mathbf{k}}_{\Ex}}
\newcommand{\kvar}{{\mathbf{k}}_{\mathbb{V}}}
\newcommand{\hatkvar}{\hat{\mathbf{k}}_{\mathbb{V}}}
\newcommand{\kmpe}{{\mathbf{k}}_{\mathrm{MPE}}}
\newcommand{\hatkmpe}{\hat{\mathbf{k}}_{\mathrm{MPE}}}
\newcommand{\kest}{\hat{\mathbf{k}}}
\newcommand{\RRE}{RRE}
\newcommand{\checkap}{{\alpha}_p}
\newcommand{\checka}{{\alpha}}
\newcommand{\checkk}{\mathbf{k}}
\newcommand{\checkkp}{{\mathbf{k}}_p}
\newcommand{\hatkp}{\hat{\mathbf{k}}_p}
\newcommand{\Kspace}{\mathbb{K}}
\newcommand{\Uspace}{\mathbb{U}}
\newcommand{\JBH}{J_{\mathrm{BH}}}
\newcommand{\JBHS}{J_{\mathrm{BHswap}}}
\DeclareMathOperator*{\esssup}{ess\,sup}
\newcommand{\arthur}[1]{{\itshape\color{cyan} ({#1})}}
\newcommand{\elise}[1]{{\itshape\color{red} ({#1})}}
\newcommand{\victor}[1]{{\itshape\color{blue}}}
\newcommand{\remove}[1]{{\color{red} {}}}
\newcommand{\added}[1]{{\color{teal} #1}}
\usepackage{url}
\usepackage{xcolor}
\definecolor{newcolor}{rgb}{.8,.349,.1}
\usepackage{bbm}
\newlength{\minisize}
\setlength{\minisize}{3cm}
\newlength{\singlecolumnsize}
\setlength{\singlecolumnsize}{9cm}
\newlength{\onehalfcolumn}
\setlength{\onehalfcolumn}{14cm}
\newlength{\fullwidth}
\setlength{\fullwidth}{19cm}
\usepackage{etoolbox}

@@

\newcommand*\linenomathpatchAMS[1]{%
  \expandafter\pretocmd\csname #1\endcsname {\linenomathAMS}{}{}%
  \expandafter\pretocmd\csname #1*\endcsname{\linenomathAMS}{}{}%
  \expandafter\apptocmd\csname end#1\endcsname {\endlinenomath}{}{}%
  \expandafter\apptocmd\csname end#1*\endcsname{\endlinenomath}{}{}%
}
\expandafter\ifx\linenomath\linenomathWithnumbers
  \let\linenomathAMS\linenomathWithnumbers
  %% The following line gets rid of an extra line numbers at the bottom:
  \patchcmd\linenomathAMS{\advance\postdisplaypenalty\linenopenalty}{}{}{}
\else
  \let\linenomathAMS\linenomathNonumbers
\fi
\linenomathpatchAMS{gather}
\linenomathpatchAMS{multline}
\linenomathpatchAMS{align}
\linenomathpatchAMS{alignat}
\linenomathpatchAMS{flalign}
\begin{document}
\linenumbers
%% Title, authors and addresses

@@

\begin{abstract}
%% Text of abstract
  Classical methods of \added{calibration}\remove{parameter estimation} usually imply the minimisation of an objective function \added{with respect to some control parameters. This function}\remove{, that} measures the error between some observations and the results obtained by a numerical model. In the presence of %uncontrollable/random nuisance
  \added{uncontrollable additional parameters that we model as} random inputs, the objective function becomes a random variable, and notions of robustness have to be introduced \added{for such an optimisation problem.}

  \remove{In this paper, we are going to present how to take into account those uncertainties by defining a family of calibration objectives based on the notion of relative-regret. with respect to the best attainable performance given the uncertainties and compare it with the minimum in the mean sense, and the minimum of variance.}

  \added{In this paper, we are going to present how to take into account those uncertainties by defining the relative-regret. This quantity allow us to compare the value of the objective function to its best performance achievable  given a realisation of the random additional parameters. By controlling this relative-regret using a probabilistic constraint, we can then define a new family of estimators, whose robustness with respect to the random inputs can be adjusted.}

\end{abstract}

@@

%----------------------------------------------------------------------------
Numerical models are widely used to study or forecast natural phenomena and improve industrial processes. However, by essence models only partially represent reality and sources of uncertainties are ubiquitous (discretisation errors, missing physical processes, poorly known boundary conditions).
%Many physical phenomena are modelled numerically in order to better understand and/or to predict their behaviour. Because of the complexity and or ignorance of the underlying physics, numerical models are imperfect representations of the reality. 
%
%Various sources of uncertainties can corrupt the model quality, such as the discretisation of the domain, or presence of  small scale phenomena that can not be fully represented. 
Moreover, such uncertainties may be of different nature. 
\cite{walker_defining_2003} proposes to consider two categories of uncertainties. On the one hand aleatoric uncertainties, coming from the inherent variability of a phenomenon, e.g.\ intrinsic randomness of some environmental variables. On the other hand, epistemic uncertainties coming from a lack of knowledge about the properties and conditions of the phenomenon underlying the behaviour of the system under study.
The latter can be accounted for through the introduction of ad-hoc correcting terms in the numerical model, that need to be properly estimated. Thus, reducing the epistemic uncertainty can be done through parameters estimation approaches. 
%when one is having observations of the reality. 
This is usually done using optimal control techniques, leading to an optimisation of a well chosen cost function which is typically built as a comparison with reference observations.
%
An application of such an approach, in the context of ocean circulation modelling, is the estimation of ocean bottom friction parameters, as done in~\cite{das_estimation_1991,das_variational_1992,boutet_estimation_2015}. \added{Moreover, as such studies are often performed at a coastal and regional scale, those models are often designed with open boundary conditions, and require external forcings, such as tidal and wind forcing. Those are then a source of aleatoric uncertainties, that should be taken into account as in~\cite{ten_brummelhuis_parameter_1990}.}
\remove{If parameters to be estimated are not the only source of uncertainties, their optimal control 
  is doomed to overfit the data, \emph{e.g} to artificially introduce errors in the controlled parameter to compensate for other sources. If such uncertainties are of aleatoric nature, then the parameter estimation is only optimal for the observed situation, and may be very poor in other configurations, phenomenon coined as \textit{localized optimisation} in~%\cite{huyse_free-form_2001}.%
}

\added{If we overlook the aleatoric uncertainties by choosing a specific outcome, the optimal control of the parameters to be estimated can lead to \emph{localized optimisation} \citep{huyse_free-form_2001} and \emph{overcalibration}, that is choosing a value that is optimal for the given situation. This value does not carry the optimality to other situations.
  In geophysics and especially in hydrological models, this overcalibration may lead to the appearance of abberations in the predictions as those uncertainties become prevalent sources of errors. In hydrology, uncertainties are the principal culprit of the existence of so called ``Hydrological monsters''~\citep{kuczera_there_2010}, that are calibrated models that perform really badly because some uncertainties in the modelling have been omitted, such as measurements errors. In flood modelling~\cite{wong_neglecting_2018}, the aleatoric uncertainty come from the structure of the model, and neglecting those uncertainties leads to underestimating hazard. In other domains as well, the aleatoric uncertainties can represent some manufacturing errors or environmental conditions such as wind direction and speed in wind turbine modelling~\cite{hu_robust_2011} or atmospheric conditions in aerospace vehicle design~\cite{brevault_contributions_2015}, thus they represent an important role in risk management.}
%A methodology based on the Hessian matrix has been described in~\cite{ribaud_krigeage_2018-1}.
%\arthur{L\`A AUSSI UNE REF SERAIT BIENVENUE}.

\added{It is then crucial to be able to take into account aleatoric uncertainties in optimisation problems. This consideration is called \textit{robust optimisation}, or also \textit{robust design} in~\cite{lelievre_consideration_2016}, or \textit{optimisation under uncertainties} \citep{petrone_robustness_2011,seshadri_density-matching_2014,cook_horsetail_2018}. Furthermore, the distinction is sometimes made between \emph{stochastic optimisation} and \emph{robust optimisation}, depending on the knowledge available on the aleatoric uncertainties.}% Présicer pbs + autres exemple avec unc aleatoric prises en compte -> flood
% \remove{Taking into account aleatoric uncertainties in optimisation problems takes several names, including \textit{robust optimisation}, \textit{robust design} in~\cite{lelievre_consideration_2016}, or \textit{optimisation under uncertainties} \citep{petrone_robustness_2011,seshadri_density-matching_2014,cook_horsetail_2018}.}

@@

%Taking into account aleatoric uncertainties while calibrating the model (reducing epistemic uncertainties) is often referred as {\it robust control problem} in the literature (see for instance, \arthur{REFs}), or optimisation under uncertainties \citep{petrone_robustness_2011, seshadri_density-matching_2014,cook_horsetail_2018}.

\remove{Let's} \added{Let us} denote $\mathbf{k} \in \Kspace$ the parameter \remove{set} to be estimated \added{in order} to reduce epistemic \remove{errors} \added{uncertainties}. \added{We assume that the aleatoric uncertainties can be modelled as a} random vector $\mathbf{U}$ whose sample space is $\Uspace$. The probability measure \added{associated with}\remove{of} $\mathbf{U}$ is $\Prob_{\mathbf{U}}$, and its density, if it exists, is $p_{\mathbf{U}}$. \added{This distribution is assumed to be known, and that it is possible to sample from it. This choice is motivated by the fact that in various applications, the aleatoric uncertainties come from expert knowledge, empirical observations, or the knowledge acquired using other models, for instance by ensemble assimilation. %  An example is functional uncertainties, where the random process can be decomposed on an orthogonal basis of random variables, which are uncorrelated and can be estimated.
  However, if it is not the case,~\cite{ning_optimization_2019} provides a comprehensive review of optimisation under uncertainty, especially on the modelling and sampling of the aleatoric uncertainties. Since the source of the aleatoric uncertainties is considered external, the choice of $\mathbf{k}$ does not have any influence on the distribution of the random variable $\mathbf{U}$, and therefore the aleatoric and epistemic uncertainties are assumed independent.
  %%%%

}

\victor{\#3 \checkmark: Did the authors implicitly assume that the aleatoric uncertainty is independent with the epistemic uncertainty? The authors should clarify this issue.}%Furthermore, $\mathbf{u}^t$ (used to generate $\mathbf{y}^{\mathrm{obs}}$) is sampled from $\mathbf{U}$.
%
The cost function $J(\mathbf{k}, \mathbf{U})$ is a random variable in this context. %, quantity of interest summarising what we aim to represent with our numerical system $J(\mathbf{k}, \mathbf{U})$ is a random variable that will be further designed as the cost function. 
It is most often defined as the squared norm of a given function $\mathcal{G}(\mathbf{k}, \mathbf{U})$% involving the numerical model.
\victor{\# 2: How should one choose and/or construct $U$ ?}
\victor{
  \begin{itemize}
  \item Control on $\mathbf{k}$ but not on $\mathbf{u}$ + examples \checkmark
  \item Misspecification and monsters \checkmark
  \item Challenging examples
  \item Give example of $J$, $\mathbf{k}$, $\mathbf{u}$
  \end{itemize}
}
\begin{linenomath*}
\begin{equation}
  \label{eq:def_cost_fun}
  J(\mathbf{k},\mathbf{U}) = \frac12\|\mathcal{G}(\mathbf{k}, \mathbf{U})\|^2
  \end{equation}
\end{linenomath*}

%$J$ is possibly complemented by a regularisation function that is omitted here for the sake of clarity. 
  For instance, in data assimilation, $J$ describes a distance between the output of the numerical model and given observed data, plus generally some regularization terms. \added{An example of such a function will be treated Section~\ref{sec:SWE_application}.}

%Calibrating the numerical models consists in the computation of $\kest$ verifying
%\begin{equation}
%  \label{eq:khat_def}
%  \kest = \argmin_{\mathbf{k} \in \Kspace} J(\mathbf{k}, \mathbf{u})
%\end{equation}
%\elise{la il y a un soucis car J(k,U) est une variable aleatoire donc on sait pas ce que ca veut dire de prendre le min} \victor{ici ça serait mieux de mettre un $\mathbf{u}^b$}
%
%where $J$ is then an objective function to minimise,
 %
%For a given $\mathbf{k}$, $J(\mathbf{k},\mathbf{U})$ is a random variable. The main point is to be able to compute a value $\mathbf{k}$ that ``minimises'' in a certain sense the random variable $J(\mathbf{k},\mathbf{U})$. \elise{a revoir. un v.a. ne se minimise pas} 
%
For a practical purpose, we assume that for every realisation $\mathbf{u}\in\Uspace$ of $\mathbf{U}$, % $\forall~ \mathbf{u}$ a realisation of $\mathbf{U}$
finding ${\mathbf{k}}_{\mathbf{u}}\in \Kspace$ that minimises the cost function $\mathbf{k}\mapsto J(\mathbf{k}, \mathbf{U}=\mathbf{u})$ is a well-posed problem, and that the optimum is unique.
Additionally, the following assumptions are made: the cost function is strictly positive, and $\forall~  \mathbf{k} \in \Kspace$, the random variable $J(\mathbf{k},\mathbf{U})$ has finite first- and second-order moments.

In this paper, we aim at finding $\kest$ a {\it robust\/} estimator of $\mathbf{k}$.
The definition of robustness differs depending on the context in which it is used. Indeed, one definition of the robustness of an estimate is a measure of the sensibility of said estimate to outliers~\citep{huber_robust_2011}. This \remove{lead}\added{leads} to the introduction of robust norms in data assimilation \citep{rao_robust_2015}. %The point of this norm is to assume Gaussian distribution for small errors (the usual $L_2$ norm), while the large errors are assumed to be Laplace distributed (so the $L_1$ norm).
In a Bayesian framework, robustness may refer to the sensitivity to a wrong specification of the priors~\citep{berger_overview_1994}. \added{As the distribution of $\mathbf{U}$ is assumed known, we are not going to consider \emph{distributional robustness}, which deals with uncertainties on the distribution of $\mathbf{U}$~\cite{rahimian_distributionally_2019}.}
